\documentclass[10pt,a4paper]{article}

% ============================================================
%  Nikhil Ranjan — Resume (compiles with XeLaTeX or LuaLaTeX)
% ============================================================

\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{microtype}

\pagestyle{empty}

% --- Color scheme: Polkadot-inspired magenta + slate ---------
\definecolor{primary}{HTML}{E6007A}
\definecolor{ink}{HTML}{1A1A2E}
\definecolor{muted}{HTML}{555566}
\definecolor{rule}{HTML}{D8D8E0}

\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    urlcolor=primary,
    citecolor=primary,
    pdftitle={Nikhil Ranjan — Resume},
    pdfauthor={Nikhil Ranjan}
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\color{ink}

% --- Section formatting ------------------------------------
\titleformat{\section}
  {\large\bfseries\color{primary}} % Removed \MakeUppercase from here
  {}{0em}{}
  [\vspace{-4pt}\color{rule}\titlerule\vspace{2pt}]

\titlespacing*{\section}{0pt}{12pt}{6pt}

% --- Custom helpers ----------------------------------------
\newcommand{\role}[4]{%
    \textbf{#1} \hfill {\color{muted}\textit{#4}}\\
    {\color{primary}\textit{#2}} \hfill {\color{muted}\small #3}\\
    \vspace{-2pt}
}

\newcommand{\edu}[5]{%
    \textbf{#1} \hfill {\color{muted}\small #2}\\
    \textit{#3} \hfill {\color{muted}\small #4}\\
    {\footnotesize #5}\\
    \vspace{4pt}
}

% Tight bullet list
\newenvironment{bullets}{%
  \begin{itemize}[leftmargin=14pt, itemsep=1pt, parsep=0pt, topsep=2pt]%
}{\end{itemize}}

\begin{document}

% ============================================================
%  Header
% ============================================================
\begin{center}
    {\Huge\bfseries Nikhil Ranjan}\\[2pt]
    {\color{muted}\small Software Architect | Rust | Polkadot | Distributed Systems}\\[6pt]
    \small
    \faMapMarker*\ Berlin, Germany \quad
    \faEnvelope\ \href{mailto:niklabh811@gmail.com}{nikhil@polkassembly.io} \quad
    \faGlobe\ \href{https://niklabh.github.io}{niklabh.github.io} \\[2pt]
    \faGithub\ \href{https://github.com/niklabh}{github.com/niklabh} \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/niklabh/}{linkedin.com/in/niklabh} \quad
    \faTwitter\ \href{https://x.com/niklabh}{x.com/niklabh}
\end{center}

% ============================================================
%  Summary
% ============================================================
\section{Summary}
Software architect with 12+ years building scalable, decentralized systems --- from founding-engineer roles at Paytm and Tokopedia to core Polkadot/Kusama infrastructure at Parity. Currently CTO and co-founder of \href{https://polkassembly.io}{\textbf{Polkassembly}}, the flagship governance platform for Polkadot \& Kusama. Deep expertise in Rust, Substrate, and WebAssembly runtimes. Creator of \href{https://github.com/niklabh/oxide}{\textbf{Oxide}} and \href{https://github.com/niklabh/velocidb}{\textbf{VelociDB}}.

% ============================================================
%  Experience
% ============================================================
\section{Experience}

\role{\href{https://polkassembly.io/}{Polkassembly}}{CTO \& Co-founder}{Aug 2021 -- Present}{Berlin}
\begin{bullets}
    \item Founded and architected Polkadot's flagship governance platform: 1,700+ referenda tracked, \$300M+ in treasury decisions facilitated, 250K+ participants.
    \item Built Rust + Substrate backends for real-time proposal analysis, validator coordination and delegated voting; integrated AI-assisted analysis and autonomous voting agents.
    \item Shipped full-stack governance flows in Next.js, TypeScript and Polkadot.js.
    \item Pioneered inscription tokens (Blobscriptions) and EVM contract deployments on Kusama.
    \item Grew the open-source organization from 1 to 20 engineers; led architecture, hiring and code review.
\end{bullets}

\role{DFINITY Foundation}{Senior Developer Relations Engineer}{Feb 2022 -- Nov 2022}{Berlin}
\begin{bullets}
    \item Supported Rust and Motoko developers building DeFi primitives and secure canister deployments on the Internet Computer.
    \item Ran the Developer Partner \& Grants program; evaluated and funded Rust-based protocol enhancements.
    \item Authored governance proposals that expanded staking participation in a \$6B+ ecosystem.
\end{bullets}

\role{Parity Technologies}{Principal Engineer}{Dec 2019 -- Jul 2021}{Berlin}
\begin{bullets}
    \item Core contributor to the launch of Polkadot and Kusama: shipped runtime/ledger code in Rust + Substrate.
    \item Implemented validator lifecycle, subnet coordination logic, and staking flows hardened for adversarial environments.
    \item Collaborated with parachain teams (e.g., Astar Network) on Substrate runtime work.
\end{bullets}

\role{Frontier Car Group}{Senior Software Engineer}{Oct 2017 -- Nov 2019}{Berlin}
\begin{bullets}
    \item Built used-car marketplaces serving emerging markets across LATAM, Africa and Asia.
\end{bullets}

\role{Tokopedia}{Senior Software Engineer}{Jan 2016 -- Sep 2017}{Delhi}
\begin{bullets}
    \item Created \textit{m.tokopedia.com} (Tokopedia Lite) --- winner of Google's Best PWA award.
\end{bullets}

\role{Paytm}{Software Engineer}{Jun 2013 -- Dec 2015}{Delhi}
\begin{bullets}
    \item Founding engineer on India's leading P2P payments platform (300M+ users); scaled microservices to 100M+ users.
\end{bullets}

% ============================================================
%  Selected Projects
% ============================================================
\section{Selected Open-Source Projects}

\textbf{\href{https://github.com/niklabh/oxide}{Oxide}} \hfill \textit{A binary-native browser in Rust.}\\
A reimagining of the web where pages are WebAssembly modules, not HTML/JS. Capability-based sandbox built on Wasmtime, Tokio and egui.

\vspace{4pt}
\textbf{\href{https://github.com/niklabh/velocidb}{VelociDB}} \hfill \textit{A modern embedded database engine in Rust.}\\
SQLite-inspired storage engine optimized for modern hardware: MVCC, async I/O on io\_uring, and SIMD vectorization.

% ============================================================
%  Education
% ============================================================
\section{Education}

\edu{Polkadot Blockchain Academy}{2023}{UC Berkeley, California}{}{Cryptography, Substrate, FRAME, Polkadot SDK, WebAssembly, decentralized networks.}

\edu{Bachelor of Technology}{2009 -- 2013}{GGSIPU, Delhi}{GPA: 7.5/10}{Applied Mathematics, Data Structures, Algorithms, Distributed Computing, Cryptography.}

% ============================================================
%  Skills
% ============================================================
\section{Skills}

\begin{bullets}
    \item \textbf{Languages:} Rust (expert), TypeScript, JavaScript, Go, Motoko, Solidity.
    \item \textbf{Blockchain \& Distributed:} Substrate, FRAME, Polkadot SDK, WASM, ICP, EVM, Staking Design, Cryptography.
    \item \textbf{Systems:} MVCC, io\_uring, Lock-free data structures, SIMD, NVMe, Sandboxing, Performance Engineering.
    \item \textbf{Web \& Data:} Next.js, React, PostgreSQL, Redis, Elasticsearch, AWS, Docker, CI/CD.
    \item \textbf{AI:} OpenAI/GPT-4 Agents, Local LLM inference, ComfyUI, Stable Diffusion.
\end{bullets}

\end{document}